Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System

### 2020-05-06 manuscript/manuscript.Rmd
include figs param

---
title: "Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System"
subtitle: A systematic review and meta-analysis
bibliography: Extras/bibliography.bib
csl: Extras/sp-basic.csl
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      phone: +1 416 946 7112
      address: 585 University Ave | Toronto, ON  M5G 2N2
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Megan Bittner BSc:
      institute: [LBFON]
      correspondence: false
  - Dan Phan BSc:
      institute: [LBFON]
      correspondence: false
  - Kristina Chang MScN:
      institute: [PMCC]
      correspondence: false
  - Navpreet Kamboj BScN:
      institute: [LBFON]
      correspondence: false
  - Elizabeth Tipton PhD:
      institute: [NW]
      correspondence: false
  - Matteo Parotto MD, PhD:
      institute: [TGH, UoT]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
  - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
  - NW: Department of Statistics, Northwestern University, Evanston, IL, United States
  - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN, Toronto, Canada
  - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto, Toronto, Canada
output:
  officedown::rdocx_document:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
always_allow_html: true
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggprisma) # https://github.com/awconway/ggprisma
library(knitr)
library(magrittr)
source(here::here("manuscript", "loa_maker.R"))
source(here::here("manuscript","meta.R"))
library(gofer) # https://github.com/awconway/gofer
library(flextable)
```

@@

ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "patients")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "perc_male")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "age")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "code")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "temp_range")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "n")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "N")

ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "patients")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "perc_male")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "age")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "code")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "temp_range")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "n")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "N")

ft <- merge_at(ft, part = "body", i=~Study=="Makinen"& 
                 patients=="Cardiac Surgery", j = "patients")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "perc_male")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "age")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "code")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "temp_range")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "N")

@@

>>>>

---
title: "Accuracy and precision of zero-heat-flux temperature measurements with the 3M^TM^ Bair Hugger^TM^ Temperature Monitoring System"
subtitle: A systematic review and meta-analysis
bibliography: Extras/bibliography.bib
csl: Extras/sp-basic.csl
author:
  - Aaron Conway PhD:
      email: aaron.conway@utoronto.ca
      phone: +1 416 946 7112
      address: 585 University Ave | Toronto, ON  M5G 2N2
      institute: [PMCC, LBFON, QUT]
      correspondence: true
  - Megan Bittner BSc:
      institute: [LBFON]
      correspondence: false
  - Dan Phan BSc:
      institute: [LBFON]
      correspondence: false
  - Kristina Chang MScN:
      institute: [PMCC]
      correspondence: false
  - Navpreet Kamboj BScN:
      institute: [LBFON]
      correspondence: false
  - Elizabeth Tipton PhD:
      institute: [NW]
      correspondence: false
  - Matteo Parotto MD, PhD:
      institute: [TGH, UoT]
      correspondence: false
institute:
  - PMCC: Peter Munk Cardiac Centre, University Health Network, Toronto, Canada
  - LBFON: Lawrence S. Bloomberg Faculty of Nursing, University of Toronto, Toronto, Canada
  - QUT: School of Nursing, Queensland University of Technology (QUT), Brisbane, Australia
  - NW: Department of Statistics, Northwestern University, Evanston, IL, United States
  - TGH: Department of Anesthesia and Pain Management, Toronto General Hospital, UHN, Toronto, Canada
  - UoT: Department of Anesthesia and Interdepartmental Division of Critical Care Medicine, University of Toronto, Toronto, Canada
output:
  officedown::rdocx_document:
    reference_docx: Extras/manuscript_template.docx
    pandoc_args:
      - --lua-filter=Extras/scholarly-metadata.lua
      - --lua-filter=Extras/author-info-blocks.lua
always_allow_html: true
params:
  include_figs: false
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(include=TRUE,
                      echo=FALSE, warning=FALSE, message=FALSE)
library(dplyr)
library(ggplot2)
library(robvis)
library(ggprisma) # https://github.com/awconway/ggprisma
library(knitr)
library(magrittr)
source(here::here("manuscript", "loa_maker.R"))
source(here::here("manuscript","meta.R"))
library(gofer) # https://github.com/awconway/gofer
library(flextable)
```

@@

ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "patients")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "perc_male")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "age")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "code")
ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "temp_range")
# ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "n")
# ft <- merge_at(ft, part = "body", i=~Study=="Iden", j = "N")

ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "patients")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "perc_male")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "age")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "code")
ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "temp_range")
# ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "n")
# ft <- merge_at(ft, part = "body", i=~Study=="Pesonen", j = "N")

ft <- merge_at(ft, part = "body", i=~Study=="Makinen"& 
                 patients=="Cardiac Surgery", j = "patients")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "perc_male")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "age")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "code")
ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "temp_range")
# ft <- merge_at(ft, part = "body", i=~Study=="Makinen", j = "N")

@@

```{r fig.cap="Fig. 1", include=params$include_figs, eval=params$include_figs}
ggprisma::ggprisma(retrieved = 131, included = 16, 
                          duplicates = 35, full_text = 23, 
                          wrong_intervention = 5, 
                          wrong_comparator = 2, 
                          wrong_design = 1, 
                          awaiting_classification = 2)
```

```{r fig.cap="Fig. 2", include=params$include_figs, eval=params$include_figs}
RoB <- data_core %>%
  dplyr::bind_rows(data_SL) %>%
  dplyr::bind_rows(data_NPA) %>%
  dplyr::select(Study, RoB_selection, RoB_spoton, RoB_comparator, RoB_flow) %>%
  dplyr::mutate(RoB_overall = dplyr::if_else(RoB_selection == "low" &
                                               RoB_spoton == "low" &
                                               RoB_comparator == "low" &
                                               RoB_flow == "low", "low", "high"))
RoB[RoB == "unclear"] <- "some concerns"
robvis::rob_traffic_light(data = RoB, tool = "QUADAS-2")
```

```{r fig.cap="Fig. 3", include=params$include_figs, eval=params$include_figs}
bias=data_core$bias
s2_unb = data_core$s2
pooled_bias = primary$bias_mean
pooled_sd = primary$sd2_est
pooled_tau2 = primary$tau_est
pooled_sd = sqrt(pooled_sd^2 + pooled_tau2)

LOA_l = primary$LOA_L
LOA_u = primary$LOA_U
LOA_l_CI = primary$CI_L_rve
LOA_u_CI = primary$CI_U_rve
g <- ggplot(data.frame(x=seq(-20,20,length=200)), aes(x=x)) + 
  stat_function(fun=dnorm, args = list(bias[1], sd=sqrt(s2_unb[1])), colour = "cornflowerblue", size=0.6, alpha = 0.5)

for (i in 2:length(bias)){
  g <- g + stat_function(fun=dnorm, args = list(bias[i], sd=sqrt(s2_unb[i])), color = "cornflowerblue", size = 0.6, alpha = 0.5)
}

g <- g + stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour ="lightcoral", alpha = 0.05) + 
  stat_function(fun=dnorm, args = list(pooled_bias, pooled_sd), colour = NA, geom="area", fill="lightcoral", alpha = 0.6) + 
  scale_x_continuous(limits = c(-3.5,3.5), breaks = c(-2, -1, 0, 1, 2)) + 
  labs(x = expression('Difference between core and ZHF temperature measurements in'*~degree*C*''),
       caption = "Blue curves are distributions of the differences between measurements from zero-heat-flux sensors and core\ntemperature measurements in individual studies. The red curve is the distribution of the pooled estimate.")+
  scale_y_continuous(name = "Density \n", limits = c(0,2.5)) +  
  #labs(title = "\nOuter confidence intervals for pooled limits of agreement\n\n  Pooled limits of agreement")+
  theme(plot.title = element_text(hjust = 0.5, margin = margin(t=10, b=-32), size=10),
        axis.text=element_text(hjust = 0.5, size=10),                                                                        
        axis.title=element_text(hjust = 0.5, size=10),
        axis.line=element_line(colour="black", size=0.2),
        panel.background = element_blank(),
        axis.ticks = element_blank(), 
        plot.caption = element_text(hjust = 0)) #+ 
#CI lines that extend to arrow tips
# geom_segment(aes(x=LOA_u, y=0, xend=LOA_u, yend=2.25), size = 0.3, linetype="dashed")+ 
# geom_segment(aes(x=LOA_l, y=0, xend=LOA_l, yend=2.25), size = 0.3, linetype="dashed")+
# geom_segment(aes(x=LOA_u_CI, y=0, xend=LOA_u_CI, yend=2.48), size = 0.3)+
# geom_segment(aes(x=LOA_l_CI, y=0, xend=LOA_l_CI, yend=2.48), size = 0.3)#+
# 
# geom_segment(aes(x=0, y=2.48, xend=LOA_u_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #R arrow high
# geom_segment(aes(x=0, y=2.48, xend=LOA_l_CI, yend=2.48), size = 0.4, arrow = arrow(length = unit(0.03, "npc")))+ #L arrow high
# geom_segment(aes(x=0, y=2.25, xend=LOA_u, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc")))+ #R arrow low
# geom_segment(aes(x=0, y=2.25, xend=LOA_l, yend=2.25), size = 0.4,  arrow = arrow(length = unit(0.03, "npc"))) #L arrow low
g
